\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-06 paper.tex
Mention we use OpenGL occlusion checks to compute visibility

\item \emph{Sees}: An important ability to know about an agent is to predict
\emph{What can it see?}, \ie what is within its field of view (FOV). Being able
to compute this information, the robot can reuse it for instance to infers
which object a human is searching for (the one that is not currently visible,
otherwise the user would not be searching for it).  In
figure~\ref{fig|spark-oro}\emph{c} the field of view of a person is
illustrated with a grey cone (broader one). While he is able to see the two
small boxes on the table in front of him, the big box on his right is out of
his FOV, and therefore, he is not able to see it.

>>>>

\item \emph{Sees}: An important ability to know about an agent is to predict
    \emph{What can it see?}, \ie what is within its field of view (FOV). Being
    able to compute this information (by dynamically placing an OpenGL camera at
    the location of the eyes and running occlusion checks from it), the robot
    can reuse it for instance to infers which object a human is searching for
    (the one that is not currently visible, otherwise the user would not be
    searching for it).  In figure~\ref{fig|spark-oro}\emph{c} the field of view
    of a person is illustrated with a grey cone (broader one). While he is able
    to see the two small boxes on the table in front of him, the big box on his
    right is out of his FOV, and therefore, he is not able to see it.
